`infercnv` results exploration for `r params$sample_id`

### 2024-10-31 analyses/cell-type-wilms-tumor-06/notebook_template/06_cnv_infercnv_exploration.Rmd

  p <- list()
  #### Plot UMAP of known Wilms tumor related alteration
  p[["compartment"]] <- visualize_metadata(infercnv_obj, "fetal_kidney_predicted.compartment", "seurat_clusters")
  #### Feature plot and repartition of the CNV per chromosome
  for(i in 1:22){
  tmp1 <- visualize_feature(infercnv_obj, feature=glue::glue("proportion_cnv_chr", i), group.by = "fetal_kidney_predicted.compartment")
  tmp2 <- visualize_density(infercnv_obj, features=glue::glue("proportion_cnv_chr", i), group.by = "fetal_kidney_predicted.compartment")
  p[[glue::glue("proportion_cnv_chr", i)]] <- tmp1 + tmp2 + plot_layout(ncol = 3, widths = c(1,2,2))
  }
  #### DotPlot
  p[["Dotplot"]] <- DotPlot(infercnv_obj, features =  colnames(infercnv_obj@meta.data)[grepl("has_cnv_chr", colnames(infercnv_obj@meta.data))], group.by = "fetal_kidney_predicted.compartment", assay = "SCT") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  #### CNV score
  meta <- infercnv_obj@meta.data
  meta$has_cnv_score <- rowSums(meta[,grepl("has_cnv_chr", colnames(meta))])
  meta$has_cnv_score[meta$has_cnv_score > cnv_threshold] <- "CNV"

>>>>

  p <- list()

  #### Plot UMAP of known Wilms tumor related alteration
  p[["compartment"]] <- visualize_metadata(infercnv_obj, "fetal_kidney_predicted.compartment", "seurat_clusters")

  #### Feature plot and repartition of the CNV per chromosome
  for(i in 1:22){
    tmp1 <- visualize_feature(infercnv_obj, feature=glue::glue("proportion_cnv_chr", i), group.by = "fetal_kidney_predicted.compartment")
    tmp2 <- visualize_density(infercnv_obj, features=glue::glue("proportion_cnv_chr", i), group.by = "fetal_kidney_predicted.compartment")
    p[[glue::glue("proportion_cnv_chr", i)]] <- tmp1 + tmp2 + plot_layout(ncol = 3, widths = c(1,2,2))
  }

  #### DotPlot
  p[["Dotplot"]] <- DotPlot(infercnv_obj, features =  colnames(infercnv_obj@meta.data)[grepl("has_cnv_chr", colnames(infercnv_obj@meta.data))], group.by = "fetal_kidney_predicted.compartment", assay = "SCT") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

  #### CNV score
  meta <- infercnv_obj@meta.data
  meta$has_cnv_score <- rowSums(meta[,grepl("has_cnv_chr", colnames(meta))])
  meta$has_cnv_score[meta$has_cnv_score > cnv_threshold] <- "CNV"
